---
title: "Mix: experience, position and usage of feature toggles"
output: rmarkdown::github_document
---

This analysis combines the experience, position and usage of feature toggles reported by the survey participants.

```{r message=FALSE, warning=FALSE, include=FALSE}
library(readr)
library(dplyr)
library(tidyr)
library(ggplot2)
```

```{r warning=FALSE}
usages_names <- data.frame(
  "long" = c(
    "Trunk-based development / WIP",
    "A/B or Mutivariate Testing",
    "Canary Releases",
    "Dark Launches",
    "Kill Switch",
    "Blue-green Deployments",
    NA
  ),
  "short" = c(
    "Trunk-based",
    "A/B",
    "Canary",
    "Dark",
    "Kill",
    "Blue-green",
    "Other"
  ))

positions_names <- data.frame(
  "long" = c(
    "Software Engineer / Developer",
    "Software Architect",
    "CTO",
    NA
  ),
  "short" = c(
    "Developer",
    "Architect",
    "CTO",
    "Other"
  ))

experiences_names <- data.frame(
  "long" = c(
    "Between 1 and 3 Years",
    "Between 4 and 5 Years",
    "More than 5 Years",
    NA
  ),
  "short" = c(
    "1 to 3",
    "4 to 5",
    "gt 5",
    "Unknown"
  ))

separator <- ";"

renameme <- function(list, names) {
  # rename, it is easier to analyze shorter texts
  reasons <- sort(unlist(strsplit(list, separator)))
  return(paste(names$short[match(reasons, names$long, nomatch = length(names$short))], collapse = separator))
}

as.usages <- function(usages) {
  return(renameme(usages, usages_names))
}

as.position <- function(positions) {
  return(renameme(positions, positions_names))
}

as.experience <- function(experiences) {
  return(renameme(experiences, experiences_names))
}

data <- read_csv("./results/Toggle Debt survey_merged_201901161456.csv",) %>%
  mutate(
    respondent = row_number(),
    experience = sapply(`How many years of professional experience do you have?`, as.experience),
    position = sapply(`How would you best describe your profession?`, as.position),
    usages = sapply(`When/for what reason do you introduce toggles in your project?`, as.usages),
  ) %>%
  dplyr::select(
    respondent,
    experience,
    position,
    usages,
  ) %>%
  separate_rows(usages, sep = ";")
```

### Heatmap
We have 3 variables, let's give a try to a heatmap:

```{r}
heatmap_data <- data %>%
  group_by(respondent, position, usages) %>%
  summarize(
    experience_scaled = case_when(
      experience == "1 to 3" ~ 1,
      experience == "4 to 5" ~ 2,
      experience == "gt 5" ~ 3,
      TRUE ~ -1 # Bang!
    ),
  )

ggplot(heatmap_data, aes(usages, position, fill = experience_scaled)) +
  geom_tile()
```

Heatmaps are not quite the way to go here. Seems like heatmaps are made for non-categorical/discrete variables.

### Multiple Correspondence Analysis

PCA or Principal Component Analysis apparently can be used for categorical variables: https://stats.stackexchange.com/a/5777/244050

TODO: Something to try

### 3-way table

```{r}
library(Hmisc)

n_respondents <- max(data$respondent)
contingency_tbl <- data %>%
  group_by(usages, experience, position) %>%
  tally() %>%
  pivot_wider(
    names_from = c("position", "experience"),
    values_from = c("n"),
    values_fill = list(n = 0),
  ) %>%
  ungroup() %>% 
  mutate(
    total = rowSums(.[-1]),
    share = round(total / n_respondents, digits = 3) * 100,
    total_share = sprintf("%d (%2.1f)", total, share),
    # usages_total_share = sprintf("%s %s", usages, total_share),
  ) %>%
  arrange(desc(share)) %>%
  select(
    usages,
    "Total Share" = total_share,
    # Reorder these
    starts_with("Developer"),
    starts_with("Architect"),
    starts_with("CTO"),
    starts_with("Other"),
  )

rownames(contingency_tbl) <- NULL

fmt <- function(names) {
  return(sub("_", "\n", names))
}

latex_tbl <- latex(
  contingency_tbl,
  # Original
  # colheads = fmt(colnames(contingency_tbl)),
  # vbar = TRUE,
  file = "table_position_experience_usages.tex",
  rowname = NULL,

  # Take 2
  cgroup = c("", "Developer", "Architect", "CTO", "Other"),
  colheads = c("Usages", "", "1 to 3", "4 to 5", "gt 5", "gt 5", "gt 5", "gt 5"),
  n.cgroup = c(2, 3, 1, 1, 1),
  first.hline.double = FALSE,
  # multicol = FALSE,
  table.env = FALSE,
  center = "none",
  # col.just = strsplit("@{}lr|ccc|c|c|c@{}", "")[[1]],
  col.just = strsplit("rrcccccccccc", "")[[1]],
)
# latex_tbl
```
