---
title: "Survival of toggles and their categories"
output: rmarkdown::github_document
---

```{r Load libraries, include=FALSE}
library(readr)
library(ggplot2)
library(dplyr)
library(tidyr)
source("./commons.R")
```

```{r Load data, include=FALSE}
data <- read_csv('../analyze/categories.csv') %>%
  mutate(repo_name = no_org(repo_name), category_comment = NULL)
```

## Toggles survival per project

How many weeks the removed and living toggles have survived?

```{r}
data %>%
  ggplot( aes(x=repo_name, y=weeks_survived, fill=repo_name) ) +
    geom_violin(scale = "width", draw_quantiles = c(0.5)) +
    geom_jitter(height = 0, width = 0.1, size = 0.5) +
    theme(
      legend.position = "none"
    ) +
    coord_flip() +
    facet_grid(cols = vars(all_routers_removed)) +
    scale_y_log10() +
    xlab("") +
    ylab("Weeks survived")
```

## Aggregated survival by categories of toggles

How do categories of removed and living toggles compare?

```{r}
data %>%
  ggplot( aes(x=category, y=weeks_survived, fill=category) ) +
    geom_violin(scale = "width", draw_quantiles = c(0.5)) +
    geom_jitter(height = 0, width = 0.1, size = 0.5) +
    coord_flip() +
    scale_y_log10() +
    facet_grid(cols = vars(all_routers_removed)) +
    theme(legend.position = "none") +
    xlab("") +
    ylab("Weeks survived")
```

## Survival time of removed toggles per category

Useful to compare toggles lifetimes. For example, is a toggle living longer than the other of the same category in a project?

```{r}
data %>%
  filter(all_routers_removed == TRUE) %>%
  ggplot( aes(x=repo_name, y=weeks_survived, fill=repo_name) ) +
    geom_violin(scale = "width", draw_quantiles = c(0.5)) +
    geom_jitter(height = 0, width = 0.1, size = 0.5) +
    coord_flip() +
    scale_y_log10() +
    facet_grid(cols = vars(category)) +
    theme(legend.position = "none") +
    xlab("") +
    ylab("Weeks survived")
```



