---
title: "Survival of toggles and their categories"
output: rmarkdown::github_document
---

```{r Load libraries, include=FALSE}
library(readr)
library(ggplot2)
library(dplyr)
library(tidyr)
library(survival)
library(GGally)
library(ggfortify)
source("./commons.R")
```

```{r Load data, include=FALSE}
data <- read_csv('../analyze/categories.csv') %>%
  mutate(repo_name = no_org(repo_name), category_comment = NULL)

edXProjects <- c("course-discovery", "ecommerce", "edx-analytics-dashboard", "edx-platform")
mozillaProjects <- c("bedrock", "kitsune", "socorro")
```

## Dataset overview
```{r}
summary(data)

data %>%
  ggplot( aes(x=category, y=weeks_survived, color=category) ) +
    geom_jitter()
```


## Toggles survival per project

How many weeks the removed and living toggles have survived?

```{r}
data %>%
  ggplot( aes(x=repo_name, y=weeks_survived, fill=repo_name) ) +
    geom_violin(scale = "width", draw_quantiles = c(0.5)) +
    geom_jitter(height = 0, width = 0.1, size = 0.5)  +
    theme(
      legend.position = "none"
    ) +
    coord_flip() +
    facet_grid(cols = vars(all_routers_removed)) +
    scale_y_log10() +
    xlab("") +
    ylab("Weeks survived")
```

Preliminary notes:

* Toggles not removed tend do live longer for most of the projects
* Some projects like tndata_backend and Jiller do not remove most of their toggles
* In general, most projects remove their toggles before 100 weeks


## Aggregated survival by categories of toggles

How do categories of removed and living toggles compare?

```{r}
data %>%
  ggplot( aes(x=category, y=weeks_survived, fill=category) ) +
    geom_violin(scale = "width", draw_quantiles = c(0.5)) +
    geom_jitter(height = 0, width = 0.1, size = 0.5) +
    coord_flip() +
    scale_y_log10() +
    facet_grid(cols = vars(all_routers_removed)) +
    theme(legend.position = "none") +
    xlab("") +
    ylab("Weeks survived")
```

Preliminary notes:

* Remaining RELEASE and OPS toggles tend to live longer than the toggles already removed
* Lifetime of RELEASE and OPS toggles distribute similarly. **Statistically different? See Kaplan-Meier analysis below**
* OPS toggles are removed earlier than RELEASE toggles


## Survival time of removed toggles per category

Useful to compare toggles lifetimes. For example, is a toggle living longer than the other of the same category in a project?

```{r}
data %>%
  # filter(repo_name == "edx-platform") %>%
  # filter(all_routers_removed == TRUE) %>%
  ggplot( aes(x=repo_name, y=weeks_survived, fill=repo_name) ) +
    geom_violin(scale = "width", draw_quantiles = c(0.5)) +
    geom_jitter(height = 0, width = 0.1, size = 0.5) +
    coord_flip() +
    scale_y_log10() +
    facet_grid(cols = vars(category), rows = vars(all_routers_removed)) +
    # facet_grid(cols = vars(category)) +
    theme(legend.position = "none") +
    xlab("") +
    ylab("Weeks survived")
```


## Kaplan-Meier estimates

Notice that from now on `data.not.unknown` will be used as data source.

```{r}
data.not.unknown <- data %>%
  filter(category != "UNKNOWN")

summary(data.not.unknown)

data.not.unknown %>%
  ggplot( aes(x=category, y=weeks_survived, color=category) ) +
    geom_jitter()
```


### Similarity of survival functions

Here's a Cox Proportional Hazards Model. This will tell us which covariates are more responsible for the removal of toggles.

```{r}
cox <- data.not.unknown %>%
  coxph(formula = Surv(weeks_survived, all_routers_removed) ~ repo_name + category, data = .)

summary(cox)

cox_fit <- survfit(cox)
autoplot(cox_fit)
```

Preliminary notes:

* Most projects significantly contribute to the removal of toggles
* Survival of toggles across projects are statistically different
* No category significantly contributes to the removal of toggles
* Are OPS and RELEASE statistically similar? In general, no. Survival curves per category are statistically similar. See "Same for all projects?" sectio below.

#### Projects of the same company

**edX projects:**
```{r}
data.not.unknown %>%
  filter(repo_name %in% edXProjects) %>%
  survdiff(Surv(.$weeks_survived, .$all_routers_removed) ~ repo_name, data = .)
```

**mozilla projects:**
```{r}
data.not.unknown %>%
  filter(repo_name %in% mozillaProjects) %>%
  survdiff(Surv(.$weeks_survived, .$all_routers_removed) ~ repo_name, data = .)
```

Preliminary notes:

* Survival of toggles in edX projects is statistically different
* Survival of toggles in mozilla projects are statistically similar



#### Same for all projects?

We know categories do not contribute for the overall survival of toggles, but now that we know we should study projects individually, this still stands for all the projects?

Following are the logrank tests to compare the survival curves. The null hypothesis is the distributions are statistically equal. Evaulate using `alpha = 0.05`

*Reminder:* if `p < alpha`, reject null hypothesis


```{r}
for (i in unique(data$repo_name)) {
  dt <- data.not.unknown %>%
    group_by(repo_name) %>%
    filter(repo_name == i & n_distinct(category) > 1)
  
  if (nrow(dt) > 1) {
    print(i)
    print(survdiff(Surv(weeks_survived, all_routers_removed) ~ category, data = dt))
    cat('\n')
  }
}
```

Preliminary notes:

* The survival times by category distributes differently in wardenclyffe, edx-platform, kitsune and tndata_backend.

**edx-platform**

```{r}
dt <- data.not.unknown %>%
  filter(repo_name == "edx-platform")

cox <- coxph(Surv(weeks_survived, all_routers_removed) ~ category, data = dt)

summary(cox)

cox_fit <- survfit(cox)
autoplot(cox_fit)
```

Preliminary notes:

* OPS does not appear in the list of covariates. *TODO: what does it mean?*
* RELEASE is significantly associated with the length of toggles survival for edx-platform


**kitsune**

```{r}
cox <- data.not.unknown %>%
  filter(repo_name == "kitsune") %>%
  coxph(formula = Surv(weeks_survived, all_routers_removed) ~ category, data = .)

summary(cox)

cox_fit <- survfit(cox)
autoplot(cox_fit)
```

Preliminary notes:

* EXPERIMENT is missing from the model. *TODO: what does it mean?*
* Toggles survive differently for OPS and RELEASE, but they do not to contribute significantly to the Cox regression model.
* Low Rsquare, the dependent and independent variables are not strongly correlated
